Risk Perceptions for Wearable Devices

### 2015-03-05 tex-inputs/results-recipient.tex
results recipient done

\subsubsection{Data Recipient}
Across all scenarios, 42\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}). A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}). However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios. But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results. Similarly, we are unaware of a more appropriate test, given our data format; Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed). Nonetheless, we repeated our analysis using only one randomly-selected data point per participant and found that our selected test was robust to this violation. Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.

{\color {red} We do not claim that there is no distinction between the friends, public, and work contact recipients, because people have been shown to behave differently, especially in the social arena (cite studies here). People are more comfortable sharing certain data types with certain recipients (refer to the table of all questions with ranks by each recipient here). There are other data types which are universally concerning, and universally unconcerning, and the magnitude of the sentiment varies by recipient. As you can see in Table (J still needs to do this table), the VUR rate for each recipient is negatively correlated with the standard deviation of the answers.  Additionally, we see that there is greater distinction between sharing people and the app server--people are comfortable sharing data they would feel uncomfortable sharing with at human recipient, and the magnitude of concerns is might more significant compared to the other recipients.}

@@

{\color {red} TODO: table of top and bottom 10 data types by recipient; refer to appendix; shoutout to when you were lying nervous or stressed work}

>>>>

\subsubsection{Data Recipient}
There was a statistically significant difference in VUR for an application's servers comparatively to human data recipients. 42\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}). A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}). However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios. But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results. Similarly, we are unaware of a more appropriate test, given our data format. Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed). Nonetheless, we repeated our analysis using only one randomly-selected data point per participant and found that our selected test was robust to this violation. Therefore, we conclude that participants were significantly more concerned about having their data seen by a human versus an application, though differences between specific human groups such as the public, friends, and work contacts were not as significant.

We do not claim that there are no distinctions between the friends, public, and work contact recipients. People are more comfortable sharing certain data types with certain human data recipients. For instance, participants were significantly uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients. Participants were much more comfortable sharing phone use and products purchased with an application server than with human recipients. Appendix \ref{sec:recipient-appendix} shows the  complete VUR and rankings of all data types by recipient.

%People have been shown to behave differently, especially in the social arena \cite{dwyer2007trust, gross2005information, fogel2009internet}.

@@

### 2015-03-05 tex-inputs/results-techrank.tex
results recipient done

We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits. We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000. To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}. We found that participants generally rated familiar technologies and those related to wearables as being low-risk. Figure~\ref{fig:techplot} depicts participants' median ratings. We found that the calibration technologies were all rated as the most risky. At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.

As a group, participants rated the familiar technologies as the most beneficial. We believe this is the result of exposure people have to these technologies---most people use these technologies daily. Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10''). People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.

{\color {red} people may have evaluated the risks only thinking of physical risk, not privacy risk. This might have happened because among the 5 presented options, the wearable-related one is the odd one out; all other options involve some physical risk scenario. These other options, by being the most prominent (4 versus 1), frame the risk perception in the user's mind as meaning "physical risk", and users may consequently ignore or downplay privacy risks. It would have been better to ask 4+4  questions (or 2+2 to keep the survey short) rather than the current 4+1. AND "with the exception of electricity, the calibration technologies were seen as lower benefit than the others". This is true for some, but not all of the others. Specifically, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial. AND The differences in risk that *are* found between the different wearable-related are not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences are negligible.}

>>>>

We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits. We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000. To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}. We found that participants generally rated technologies related to wearables as being low-risk comparatively to other technologies (Figure \ref{fig:techplot}). Appendix ~\ref{sec:riskben-appendix} shows participants' median, quartiles, and distributions of risks and benefit ratings for all technologies. We found that the calibration technologies, which were more familiar to the participants, were all rated as the most risky.

As a group, participants rated more familiar technologies as the more beneficial. We believe this is the result of exposure people have to these technologies---most people use these technologies daily and therefore see what the benefits of these technologies are. It is true that people perceive unfamiliar technologies as less beneficial at the moment, but this will change as the use of these technologies evolve and adoption increases. Most calibration technologies, with the exception of electricity, were seen as lower benefit than the others. However, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.

Of the wearable technologies, privacy-invasive ones were perceived to be risky. Top risky technologies include facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal,  equivalent risk levels (i.e., a median of ``10''). The differences in risk that found between the different wearable-related technologies, are not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences are negligible. Interestingly, privacy risks and are comparative to real physical risks; for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.

People prompted to rate with respect to all considerations (see ~\ref{sec:prompt}), including physical harm risk to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life, people may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk. Among the 5 presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk to the users.

### 2015-03-05 tex-inputs/riskben.tex
results recipient done

\section{Risk and Benefit Perceptions of Wearables Capabilities}
\label{sec:riskben-appendix}

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Gender Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionben} \\ 
Age Detection & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionben} \\ 
Discreet Microphone & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophoneben} \\ 
Cubetastic & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticben} \\ 
Fitness Trackers & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersben} \\ 
Voice Based Emotion Detection & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionben} \\ 
Facial Detection & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionben} \\ 
Discreet Video Camera & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocameraben} \\ 
Google Glass & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassben} \\ 
Smartwatches & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesben} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleBenefit} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunBenefit} \\ 
Facial Recognition & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionben} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerBenefit} \\ 
Speech To Text & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextben} \\ 
Voice Recognition & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionben} \\ 
Language Detection & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionben} \\ 
Heart Rate Detection & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionben} \\ 
Location Tracking & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingben} \\ 
Email & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailben} \\ 
Smartphones & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesben} \\ 
Laptops & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsben} \\ 
Internet & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetben} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityBenefit} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} \\ 
Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} \\ 
Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} \\ 
Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} \\ 
Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} \\ 
Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} \\ 
Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} \\ 
Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} \\ 
Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} \\ 
Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} \\ 
Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} \\ 
Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} \\ 
Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} \\ 
Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} \\ 
Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} \\ 
Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} \\ 
Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} \\ 
Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} \\ 
Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} \\ 
Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

>>>>

\section{Risk Benefit Assessments of Various Technologies}
\label{sec:riskben-appendix}

\begin{table}[h!!!!]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} \\ 
Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} \\ 
Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} \\ 
Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} \\ 
Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} \\ 
Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} \\ 
Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} \\ 
Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} \\ 
Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} \\ 
Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} \\ 
Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} \\ 
Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} \\ 
Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} \\ 
Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} \\ 
Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} \\ 
Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} \\ 
Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} \\ 
Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} \\ 
Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} \\ 
Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk} \\ 
\hline
\end{tabular}
\caption{Risk rankings in response to the Fischoff-style prompt for various technologies and capabilities.Most technologies are capabilities with respect to wearable devices. Calibration technologies were electricity, guns, lawnmowers, and motorcycles. Wearable technologies included the Google Glass and the Cubetastic3000. Other specific technologies, such as internet, email, laptops, and smartphones, were also asked.}
\label{risk}
\end{center}
\end{table}

\begin{table}[h!!!!!]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Gender Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionben} \\ 
Age Detection & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionben} \\ 
Discreet Microphone & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophoneben} \\ 
Cubetastic & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticben} \\ 
Fitness Trackers & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersben} \\ 
Voice Based Emotion Detection & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionben} \\ 
Facial Detection & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionben} \\ 
Discreet Video Camera & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocameraben} \\ 
Google Glass & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassben} \\ 
Smartwatches & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesben} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleBenefit} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunBenefit} \\ 
Facial Recognition & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionben} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerBenefit} \\ 
Speech To Text & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextben} \\ 
Voice Recognition & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionben} \\ 
Language Detection & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionben} \\ 
Heart Rate Detection & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionben} \\ 
Location Tracking & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingben} \\ 
Email & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailben} \\ 
Smartphones & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesben} \\ 
Laptops & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsben} \\ 
Internet & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetben} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityBenefit} \\ 
\hline
\end{tabular}
\caption{Benefit rankings in response to the Fischoff-style prompt for various technologies and capabilities. Most technologies are capabilities with respect to wearable devices. Calibration technologies were electricity, guns, lawnmowers, and motorcycles. Wearable technologies included the Google Glass and the Cubetastic3000. Other specific technologies, such as internet, email, laptops, and smartphones, were also asked. }
\label{benefit}
\end{center}
\end{table}
